\thetitle

### 2020-11-21 writing/introduction.tex
Fix missing section label, number of scenarios

The paper's second contribution is a set of results from applying the evaluation
method to three distinct blame assignment strategies and approximately
722,000 cases (section~\ref{sec:results}): Vitousek et
al.'s strategy of tracking typed/untyped boundaries in Reticulated, called Transient;
Tobin-Hochstadt et al.'s use of higher-order contract system~\cite{ff-icfp-2002,
mf-toplas-2009}, called Natural; and the approach of industrial systems that forego blame
and instead rely on error messages from the
underlying programming language, called Erasure. A direct interpretation of the results
(section~\ref{sec:discussion}) is that
they validate the conjecture behind the work of theoreticians. A good blame assignment
strategy helps the search for impedance mismatches between the specified types
and the behavior of untyped components.
Furthermore, the evaluation method
identifies the wrapper-based blame tracking of Typed Racket as the most
useful approach, with that of Reticulated Python close behind.

>>>>

The paper's second contribution is a set of results from applying the evaluation
method to three distinct blame assignment strategies and approximately
72,200 cases (section~\ref{sec:results}): Vitousek et
al.'s strategy of tracking typed/untyped boundaries in Reticulated, called Transient;
Tobin-Hochstadt et al.'s use of higher-order contract system~\cite{ff-icfp-2002,
mf-toplas-2009}, called Natural; and the approach of industrial systems that forego blame
and instead rely on error messages from the
underlying programming language, called Erasure. A direct interpretation of the results
(section~\ref{sec:discussion}) is that
they validate the conjecture behind the work of theoreticians. A good blame assignment
strategy helps the search for impedance mismatches between the specified types
and the behavior of untyped components.
Furthermore, the evaluation method
identifies the wrapper-based blame tracking of Typed Racket as the most
useful approach, with that of Reticulated Python close behind.
